% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Current} {LinkedIn | Senior Site Reliability Engineer} {SRE} {Sunnyvale CA - Portland OR / Hybrid}
    {Auguest 2018}    {
    At LinkedIn on the Media-SRE team, we launched the infrastructure powering all images,
video, live video and documents for LinkedIn worldwide, which handle a sustained ~2M
QPS. Media-SRE work with three teams of 20+ developers to maintain the stability of, and
defensively scale, all media platforms processing and serving media artifacts for our 850M members.
The SRE role involves working as an individual contributor empowered to develop, lead and organize impactful changes in capacity planning, automation of deployments and upgrades, disaster recovery, code-reviews, tool building and detailed experiments and tests of new features, all with extensive monitoring and alerting.
                    }
                    {pandas, Apache Kafka, Java, Python, AWS}
  \emptySeparator
  \experience
    {March 2018} {Westrock | Senior DevOps Engineer} {DevOps}  {Atlanta GA}
    {August 2018}    {
                      As a Senior DevOps engineer at Westrock I was the point person on the team for the
company cloud initiative and was consulted for tools and cloud methods by various teams
(or, centers of excellence, CoE's) within the company. I worked with several teams of data
engineers to streamline their code and data ingests of automated tools for mill profitability
and enterprise sales data. We used a mix of Jenkins and AWS data pipelines to orchestrate
spark and sqoop jobs in EMR.
                    }
                    {Spark, Python, Jenkins, AWS, Sqoop, EMR, MySQL, Docker}
  \emptySeparator
  \experience
    {October 2015} {Rx Marketing | Vice President, Technology} {VP}  {Santa Monica - Costa Rica - Venice - Atlanta}
    {March 2018}    {
                      As Vice President of Technology I architected a custom scalable system of delivery for
opt-in email campaigns, auto and home refinance and loans among a variety of marketing
pillars connecting over thirty third-party partners. I hired and managed a small team to built
out a REST API and systems used for RXMG for millions of contacts and leads per month.
This system was 100\% in AWS auto-scaling groups using PHP7 OOP (Laravel), Nginx,
HAProxy, Docker, Galera Cluster all on Ubuntu. The AWS services used in creation are EC2, S3, SQS, ELB, ECS, SES, R53, ElastiCache, Lambda, Kinesis (for CEP), EFS and RDS-Aurora.
                    }
                    {AWS, MySQL, PHP, Nginx, HAProxy, Docker, CEP}
  \emptySeparator
\end{experiences}
